Agents and you, a brief summary

### 2015-11-03 agents/summery.tex
added most of the basics of KRIPKE!!!

\begin{tabular}{ll}
	Symbol & Definition \\ \toprule
	% worlds implies mutability, states, well a state is by definition 
	% imutable. I'm pretty sure we want immutability in these kind 
	% off logics
	$S$ & Is a set of \emph{states (or worlds)} \\
	$\pi$ & Is a truth assignment function $\pi : S \times AT \to {tt, ff}$ \\
	$R$	& $R \subseteq S \times S$ is an \emph{accesibility relation}
\end{tabular}

>>>>

\begin{tabular}{ll}
	Symbol & Definition \\ \toprule
	% worlds implies mutability, states, well a state is by definition 
	% imutable. I'm pretty sure we want immutability in these kind 
	% off logics
	$S$ & Is a set of \emph{states (or worlds)} \\
	$\pi$ & Is a truth assignment function $\pi : S \times AT \to {tt, ff}$ \\
	$R$	& $R \subseteq S \times S$ is an \emph{accesibility relation}\\
\end{tabular}

\subsubsection{Interpertation}

\begin{center}
\begin{tikzpicture}[auto, >=stealth', auto, semithick, node distance=3cm]
\tikzstyle{every state}=[fill=white,draw=black,thick,text=black,scale=1]
\node[state]    (S)            {$\neg p, q$};
\node[state]    (A)[below of=S]{$p, \neg q$};
\node[state]    (B)[right of=S]{$\neg p, \neg q$};
\node[state]    (C)[right of=B]{$p, q$};
\node[state]    (E)[below of=B]{$\neg p, q$};
\path
(S)   edge[above]     		(A)
(S)   edge[above]     		(E)
(S)   edge[above]     		(B)
(B)    edge[above]     		(E)
(E)    edge[above]     		(C);
\end{tikzpicture}
\end{center}

Like classical propositional logic, but now realtive to a model and a state:

\[ M,s \vDash \phi \]

thus:

\begin{tabular}{lll}
	Modal & $\Leftrightarrow$ & Interpertation \\ \toprule
$M,s \vDash p$ & $\Leftrightarrow$ & $\pi(s,p) = tt$ \\
$M,s \vDash \phi \wedge \varphi $ & $\Leftrightarrow$ & $ M,s \vDash \phi
\mbox{ and }M,s\vDash \varphi$ \\
$M,s \vDash \Box \phi $ & $\Leftrightarrow$ & $ M,t \vDash \phi $ for 
\emph{every} $t$ such that $R(s,t)$ \\
$M,s \vDash \Diamond \phi $ & $\Leftrightarrow$ & $ M,t \vDash \phi $ for 
\emph{some} $t$ such that $R(s,t)$ \\
\end{tabular}

\subsubsection{Validity}
\begin{tabular}{llll}
	Definition & Denotation & $\Leftrightarrow$ & Interpertation \\ \toprule

$\phi$ is \emph{valid} in a model $M= \langle S, \pi, R \rangle$ &
$M\vDash\phi$ & $\Leftrightarrow$ & $M,s \vDash \phi$ for all $s \in S$ \\

$\phi$ is \emph{valid}  &
$\vDash\phi$ & $\Leftrightarrow$ & $M\vDash\phi$ for all Kripke models $M$ \\

$\phi$ is \emph{valid} wrt class $\zeta$ &
$\zeta\vDash\phi$ & $\Leftrightarrow$ & $M\vDash\phi$ for all Kripke models
$M \in \zeta$ \\
\end{tabular}

The last one doesn't occur often.

\subsection{System K}
We try to  axiomatize validities.

\paragraph{Axioms} We import all (or enough) propositional tautologies.
The K axiom ($(\Box\phi \wedge \Box (\phi \to \varphi))\to\Box\varphi$) is added.

\paragraph{Rules} Modes ponens
\begin{prooftree}
	\AxiomC{$\phi$}
	\AxiomC{$\phi \to \varphi$}
	\BinaryInfC{$\varphi$}
\end{prooftree}

Necisitation rule:
\begin{prooftree}
	\AxiomC{$\phi$}
	\UnaryInfC{$\Box\phi$}
\end{prooftree}
